%!TEX root = ../hutbthesis_main.tex
\chapter*{参考文献}
\addcontentsline{toc}{chapter}{参考文献}
\begin{enumerate}[label={[\arabic*]},leftmargin=2.2em,itemsep=0.2em]
  \item FAA. Towbar and Towbarless Movement of Aircraft: Advisory Circular AC 00-65A[R]. Washington, DC: Federal Aviation Administration, 2023.
  \item 孙艳坤，张威，杨雄伟，刘佳辉，朱海军，刘宇轩，秦嘉浩. 飞机牵引滑行技术综述[J]. 交通运输工程学报，2023，23(3)：23-43.
  \item 中国民用航空局. 民用机场地面活动引导与控制系统（SMGCS）建设和运行指南[R]. 北京：中国民用航空局，2024.
  \item MH/T 4042—2023，高级场面活动引导与控制系统技术规范[S]. 北京：中国民用航空局，2023.
  \item ICAO. Advanced Surface Movement Guidance and Control Systems (A-SMGCS) Manual: Doc 9830 AN/452[R]. Montreal: International Civil Aviation Organization, 2004.
  \item EUROCONTROL. EUROCONTROL Specification for Advanced-Surface Movement Guidance and Control System (A-SMGCS) Services: SPEC-171[R]. Brussels: EUROCONTROL, 2020.
  \item 孙艳坤，杨慧，张威，秦嘉浩. 飞机牵引滑行入港安全运动路径生成及其轨迹跟踪控制方法[J]. 交通信息与安全，2022，40(5)：91-101.
  \item 张军，黄明辉，王玥琳，阳星，叶敏，贾永乐. 基于MPC的飞机牵引车轨迹跟踪[J]. 北京航空航天大学学报，2025，51(9)：2916-2926.
  \item 张军，文川，阳星，等. 基于ADRC的电传动飞机牵引车控制系统设计[J]. 北京航空航天大学学报，2023，49(5)：1017-1026.
  \item ZANINOTTO S, GAUCI J, ZAMMIT B. An Autonomous Tow Truck Algorithm for Engineless Aircraft Taxiing[J]. Aerospace, 2024, 11(4):307.
  \item ZOUTENDIJK M, MITICI M, HOEKSTRA J M. An investigation of operational management solutions and challenges for electric taxiing of aircraft[J]. Research in Transportation Business \& Management, 2023, 49:101019.
  \item ZOUTENDIJK M, MITICI M. Fleet scheduling for electric towing of aircraft under limited airport energy capacity[J]. Energy, 2024, 294:130924.
  \item BILIAKOVYCH O, KHARCHENKO O. The concept of an unmanned airport tug as an alternative to traditional aircraft tugs[J]. Modern Engineering and Innovative Technologies, 2023, 1(28-01):69-73.
  \item QUIGLEY M, CONLEY K, GERKEY B, FAUST J, FOOTE T, LEIBS J, WHEELER R, NG A. ROS: an open-source Robot Operating System[A]. ICRA Workshop on Open Source Software[C]. Kobe: IEEE, 2009：1-6.
  \item KOENIG N, HOWARD A. Design and use paradigms for Gazebo, an open-source multi-robot simulator[A]. Proceedings of the 2004 IEEE/RSJ International Conference on Intelligent Robots and Systems[C]. Sendai: IEEE, 2004：2149-2154.
  \item 王雅清，倪晓昌，李静，周杰，杜博文. 移动机器人路径规划算法研究进展[J]. 智能计算机与应用，2024，14(11)：211-216.
  \item 霍凤财，迟金，黄梓健，任璐，孙勤江，陈建玲. 移动机器人路径规划算法综述[J]. 吉林大学学报：信息科学版，2018，36(6)：639-647.
  \item 龚建伟，姜岩，徐威. 无人驾驶车辆模型预测控制[M]. 北京：北京理工大学出版社，2014.
  \item Open Source Robotics Foundation. Gazebo ROS control tutorial[EB/OL]. https://classic.gazebosim.org/tutorials?tut=ros\_control, 2026-05-06.
  \item ROS Wiki. Adding Physical and Collision Properties to a URDF Model[EB/OL]. https://wiki.ros.org/urdf/Tutorials/Adding\%20Physical\%20and\%20Collision\%20Properties\%20to\%20a\%20URDF\%20Model, 2026-05-06.
  \item ROS Index. xacro: XML Macros[EB/OL]. https://index.ros.org/p/xacro/, 2026-05-06.
  \item 赵景波，朱梁鹏，刘成晔. 四轮转向智能车辆路径跟踪控制策略研究[J]. 系统仿真学报，2021，33(10)：2390-2398.
  \item 毛丁丁，邓亚东. 四轮转向智能车辆轨迹跟踪及稳定控制研究[J]. 机械科学与技术，2020，39(7)：1094-1099.
  \item ROS Index. gazebo\_ros\_control: Gazebo ros\_control Interfaces[EB/OL]. https://index.ros.org/p/gazebo\_ros\_control/, 2026-05-06.
  \item SIEGWART R, NOURBAKHSH I R, SCARAMUZZA D. Introduction to Autonomous Mobile Robots[M]. 2nd ed. Cambridge: MIT Press, 2011：13-120.
  \item THRUN S, BURGARD W, FOX D. Probabilistic Robotics[M]. Cambridge: MIT Press, 2005：1-672.
  \item RAJAMANI R. Vehicle Dynamics and Control[M]. 2nd ed. New York: Springer, 2012：15-165.
  \item LAVALLE S M. Planning Algorithms[M]. Cambridge: Cambridge University Press, 2006：1-826.
  \item LATOMBE J C. Robot Motion Planning[M]. Norwell: Kluwer Academic Publishers, 1991：1-672.
  \item HART P E, NILSSON N J, RAPHAEL B. A formal basis for the heuristic determination of minimum cost paths[J]. IEEE Transactions on Systems Science and Cybernetics, 1968, 4(2):100-107.
  \item DIJKSTRA E W. A note on two problems in connexion with graphs[J]. Numerische Mathematik, 1959, 1(1):269-271.
  \item LAVALLE S M, KUFFNER J J. Randomized kinodynamic planning[J]. The International Journal of Robotics Research, 2001, 20(5):378-400.
  \item FOX D, BURGARD W, THRUN S. The dynamic window approach to collision avoidance[J]. IEEE Robotics \& Automation Magazine, 1997, 4(1):23-33.
  \item COULTER R C. Implementation of the Pure Pursuit Path Tracking Algorithm[R]. Pittsburgh: Carnegie Mellon University Robotics Institute, 1992.
  \item HOFFMANN G M, TOMLIN C J, MONTEMERLO M, THRUN S. Autonomous automobile trajectory tracking for off-road driving: controller design, experimental validation and racing[A]. Proceedings of the 2007 American Control Conference[C]. New York: IEEE, 2007：2296-2301.
  \item PADEN B, ČÁP M, YONG S Z, YERSHOV D, FRAZZOLI E. A survey of motion planning and control techniques for self-driving urban vehicles[J]. IEEE Transactions on Intelligent Vehicles, 2016, 1(1):33-55.
  \item BRADSKI G. The OpenCV Library[J]. Dr. Dobb’s Journal of Software Tools, 2000, 25(11):120-125.
  \item OLSON E. AprilTag: A robust and flexible visual fiducial system[A]. Proceedings of the 2011 IEEE International Conference on Robotics and Automation[C]. Shanghai: IEEE, 2011：3400-3407.
\end{enumerate}
