%!TEX root = ../hutbthesis_main.tex
\begin{thebibliography}{99}
\bibitem{ref1} FAA. Towbar and Towbarless Movement of Aircraft: Advisory Circular AC 00-65A{[}R{]}. Washington, DC: Federal Aviation Administration, 2023.
\bibitem{ref2} 孙艳坤，张威，杨雄伟，刘佳辉，朱海军，刘宇轩，秦嘉浩. 飞机牵引滑行技术综述{[}J{]}. 交通运输工程学报，2023，23(3)：23-43.
\bibitem{ref3} 中国民用航空局. 民用机场地面活动引导与控制系统（SMGCS）建设和运行指南{[}R{]}. 北京：中国民用航空局，2024.
\bibitem{ref4} MH/T 4042---2023，高级场面活动引导与控制系统技术规范{[}S{]}. 北京：中国民用航空局，2023.
\bibitem{ref5} ICAO. Advanced Surface Movement Guidance and Control Systems (A-SMGCS) Manual: Doc 9830 AN/452{[}R{]}. Montreal: International Civil Aviation Organization, 2004.
\bibitem{ref6} EUROCONTROL. EUROCONTROL Specification for Advanced-Surface Movement Guidance and Control System (A-SMGCS) Services: SPEC-171{[}R{]}. Brussels: EUROCONTROL, 2020.
\bibitem{ref7} 孙艳坤，杨慧，张威，秦嘉浩. 飞机牵引滑行入港安全运动路径生成及其轨迹跟踪控制方法{[}J{]}. 交通信息与安全，2022，40(5)：91-101.
\bibitem{ref8} 张军，黄明辉，王\CJKfallbackchar{玥}琳，阳星，叶敏，贾永乐. 基于MPC的飞机牵引车轨迹跟踪{[}J{]}. 北京航空航天大学学报，2025，51(9)：2916-2926.
\bibitem{ref9} 张军，文川，阳星，等. 基于ADRC的电传动飞机牵引车控制系统设计{[}J{]}. 北京航空航天大学学报，2023，49(5)：1017-1026.
\bibitem{ref10} ZANINOTTO S, GAUCI J, ZAMMIT B. An Autonomous Tow Truck Algorithm for Engineless Aircraft Taxiing{[}J{]}. Aerospace, 2024, 11(4):307.
\bibitem{ref11} ZOUTENDIJK M, MITICI M, HOEKSTRA J M. An investigation of operational management solutions and challenges for electric taxiing of aircraft{[}J{]}. Research in Transportation Business \& Management, 2023, 49:101019.
\bibitem{ref12} ZOUTENDIJK M, MITICI M. Fleet scheduling for electric towing of aircraft under limited airport energy capacity{[}J{]}. Energy, 2024, 294:130924.
\bibitem{ref13} BILIAKOVYCH O, KHARCHENKO O. The concept of an unmanned airport tug as an alternative to traditional aircraft tugs{[}J{]}. Modern Engineering and Innovative Technologies, 2023, 1(28-01):69-73.
\bibitem{ref14} QUIGLEY M, CONLEY K, GERKEY B, FAUST J, FOOTE T, LEIBS J, WHEELER R, NG A. ROS: an open-source Robot Operating System{[}A{]}. ICRA Workshop on Open Source Software{[}C{]}. Kobe: IEEE, 2009：1-6.
\bibitem{ref15} KOENIG N, HOWARD A. Design and use paradigms for Gazebo, an open-source multi-robot simulator{[}A{]}. Proceedings of the 2004 IEEE/RSJ International Conference on Intelligent Robots and Systems{[}C{]}. Sendai: IEEE, 2004：2149-2154.
\bibitem{ref16} 王雅清，倪晓昌，李静，周杰，杜博文. 移动机器人路径规划算法研究进展{[}J{]}. 智能计算机与应用，2024，14(11)：211-216.
\bibitem{ref17} 霍凤财，迟金，黄梓健，任璐，孙勤江，陈建玲. 移动机器人路径规划算法综述{[}J{]}. 吉林大学学报：信息科学版，2018，36(6)：639-647.
\bibitem{ref18} 龚建伟，姜岩，徐威. 无人驾驶车辆模型预测控制{[}M{]}. 北京：北京理工大学出版社，2014.
\bibitem{ref19} Open Source Robotics Foundation. Gazebo ROS control tutorial{[}EB/OL{]}. \href{https://classic.gazebosim.org/tutorials?tut=ros_control}{https://classic.gazebosim.org/tutorials?tut=ros\_control}, 2026-05-06.
\bibitem{ref20} ROS Wiki. Adding Physical and Collision Properties to a URDF Model{[}EB/OL{]}. \href{https://wiki.ros.org/urdf/Tutorials/Adding\%20Physical\%20and\%20Collision\%20Properties\%20to\%20a\%20URDF\%20Model}{https://wiki.ros.org/urdf/Tutorials/Adding\%20Physical\%20and\%20Collision\%20Properties\%20to\%20a\%20URDF\%20Model}, 2026-05-06.
\bibitem{ref21} ROS Index. xacro: XML Macros{[}EB/OL{]}. \href{https://index.ros.org/p/xacro/}{https://index.ros.org/p/xacro/}, 2026-05-06.
\bibitem{ref22} 赵景波，朱梁鹏，刘成晔. 四轮转向智能车辆路径跟踪控制策略研究{[}J{]}. 系统仿真学报，2021，33(10)：2390-2398.
\bibitem{ref23} 毛丁丁，邓亚东. 四轮转向智能车辆轨迹跟踪及稳定控制研究{[}J{]}. 机械科学与技术，2020，39(7)：1094-1099.
\bibitem{ref24} ROS Index. gazebo\_ros\_control: Gazebo ros\_control Interfaces{[}EB/OL{]}. \href{https://index.ros.org/p/gazebo_ros_control/}{https://index.ros.org/p/gazebo\_ros\_control/}, 2026-05-06.
\bibitem{ref25} SIEGWART R, NOURBAKHSH I R, SCARAMUZZA D. Introduction to Autonomous Mobile Robots{[}M{]}. 2nd ed. Cambridge: MIT Press, 2011：13-120.
\bibitem{ref26} THRUN S, BURGARD W, FOX D. Probabilistic Robotics{[}M{]}. Cambridge: MIT Press, 2005：1-672.
\bibitem{ref27} RAJAMANI R. Vehicle Dynamics and Control{[}M{]}. 2nd ed. New York: Springer, 2012：15-165.
\bibitem{ref28} LAVALLE S M. Planning Algorithms{[}M{]}. Cambridge: Cambridge University Press, 2006：1-826.
\bibitem{ref29} LATOMBE J C. Robot Motion Planning{[}M{]}. Norwell: Kluwer Academic Publishers, 1991：1-672.
\bibitem{ref30} HART P E, NILSSON N J, RAPHAEL B. A formal basis for the heuristic determination of minimum cost paths{[}J{]}. IEEE Transactions on Systems Science and Cybernetics, 1968, 4(2):100-107.
\bibitem{ref31} DIJKSTRA E W. A note on two problems in connexion with graphs{[}J{]}. Numerische Mathematik, 1959, 1(1):269-271.
\bibitem{ref32} LAVALLE S M, KUFFNER J J. Randomized kinodynamic planning{[}J{]}. The International Journal of Robotics Research, 2001, 20(5):378-400.
\bibitem{ref33} FOX D, BURGARD W, THRUN S. The dynamic window approach to collision avoidance{[}J{]}. IEEE Robotics \& Automation Magazine, 1997, 4(1):23-33.
\bibitem{ref34} COULTER R C. Implementation of the Pure Pursuit Path Tracking Algorithm{[}R{]}. Pittsburgh: Carnegie Mellon University Robotics Institute, 1992.
\bibitem{ref35} HOFFMANN G M, TOMLIN C J, MONTEMERLO M, THRUN S. Autonomous automobile trajectory tracking for off-road driving: controller design, experimental validation and racing{[}A{]}. Proceedings of the 2007 American Control Conference{[}C{]}. New York: IEEE, 2007：2296-2301.
\bibitem{ref36} PADEN B, ČÁP M, YONG S Z, YERSHOV D, FRAZZOLI E. A survey of motion planning and control techniques for self-driving urban vehicles{[}J{]}. IEEE Transactions on Intelligent Vehicles, 2016, 1(1):33-55.
\bibitem{ref37} BRADSKI G. The OpenCV Library{[}J{]}. Dr. Dobb's Journal of Software Tools, 2000, 25(11):120-125.
\bibitem{ref38} OLSON E. AprilTag: A robust and flexible visual fiducial system{[}A{]}. Proceedings of the 2011 IEEE International Conference on Robotics and Automation{[}C{]}. Shanghai: IEEE, 2011：3400-3407.
\end{thebibliography}
