\keywordsen{Muscle-driven, Biomechanics, MuJoCo, Human-Computer Interaction, Steering Wheel Control, Precision Test}
\begin{abstracten}

This thesis focuses on the muscle-driven biomechanical human-computer interaction (HCI) system and designs a steering wheel control system with visual guidance based on the MuJoCo simulation platform. Firstly, the domestic and foreign research status of biomechanical modeling, muscle-driven control, visual guidance and HCI accuracy evaluation is reviewed, and the limitations of existing technologies in generalization, individual adaptation and low-cost simulation are clarified. Secondly, based on the upper limb muscle-skeleton dynamics, a human dual-arm model and a steering wheel physical model are built with MuJoCo, and the coupling drive from muscle activation to steering wheel angle is realized. Then, an adaptive nonlinear mapping algorithm and a real-time visual guidance feedback module are designed to achieve smooth control from muscle force to steering wheel rotation. Finally, the system is verified by functional test, accuracy test, stability test and usability test, using MAE, RMSE, response delay and continuous running stability as indicators. The experimental results show that the mean absolute error of steering wheel angle tracking is less than 3$^\circ$, the response delay is lower than 10 ms, and there is no obvious drift after 1 hour of continuous operation. The system can stably complete the steering wheel control task under visual guidance. This research can provide a lightweight and highly biocompatible HCI solution for driving simulation, rehabilitation training, industrial collaborative manipulation and other scenarios.

\end{abstracten}